Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-27 doc/tables/realdata.tex
Paper and defence presentation updates

\begin{tabular}{ccccc}
  Reference & Sequences ($n$) & Location & Risk group & Gene \\
  \hline
  \textcite{wang2015targeting} & 173 & Beijing, China & MSM & \textit{pol} \\
  \textcite{cuevas2009hiv} & 287 & Basque Country, Spain & mixed & \textit{pol} \\
  \textcite{novitsky2013phylogenetic} & \multirow{2}{*}{180} &
  \multirow{2}{*}{Mochudi, Botswana} & \multirow{2}{*}{HET} &
  \multirow{2}{*}{\textit{env}} \\ \textcite{novitsky2014impact} \\
  \textcite{li2015hiv} & 280 & Shanghai, China & MSM & \textit{pol} \\
  \textcite{niculescu2015recent} & 136 & Romania & IDU & \textit{pol} \\
  \hline
\end{tabular}

>>>>

\begin{tabular}{ccccc}
  Reference & Sequences ($n$) & Location & Risk group & Gene \\
  \hline
  \textcite{zetterberg2004two} & 171/188 & Estonia & IDU & \textit{env}/\textit{gag} \\
  \textcite{niculescu2015recent} & 136 & Romania & IDU & \textit{pol} \\
  \textcite{novitsky2013phylogenetic} & \multirow{2}{*}{180} &
  \multirow{2}{*}{Mochudi, Botswana} & \multirow{2}{*}{HET} &
  \multirow{2}{*}{\textit{env}} \\ \textcite{novitsky2014impact} \\
  \textcite{mccormack2002early} & 141/154 & Karonga District, Malawi & HET & \textit{env}/\textit{gag} \\
  \textcite{grabowski2014role} & 225 & Rakai District, Uganda & HET & \textit{env}/\textit{gag} \\
  \textcite{wang2015targeting} & 173 & Beijing, China & MSM & \textit{pol} \\
  \textcite{kao2011surveillance} & 275 & Taiwan & MSM & \textit{pol} \\
  \textcite{little2014using} & 180 & San Fransisco, USA & MSM & \textit{pol} \\
  \textcite{li2015hiv} & 280 & Shanghai, China & MSM & \textit{pol} \\
  \textcite{cuevas2009hiv} & 287 & Basque Country, Spain & mixed & \textit{pol} \\
  \hline
\end{tabular}

### 2016-06-27 doc/thesis/appendix.Rnw
Paper and defence presentation updates

\begin{figure}[ht]
    \includegraphics{bctree-posterior}
    \caption
    [
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Canada data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Canada data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:bctree}
\end{figure}

\begin{figure}[ht]
    \includegraphics{cuevas2009-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to mixed/Spain data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to mixed/Spain data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:cuevas}
\end{figure}

\begin{figure}[ht]
    \includegraphics{grabowski2014-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Uganda data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Uganda data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:grabowski}
\end{figure}

\begin{figure}[ht]
    \includegraphics{kao2011-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Taiwan data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Taiwan data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:kao}
\end{figure}

\begin{figure}[ht]
    \includegraphics{li2015-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Shanghai data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Shanghai data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density. 
    }
    \label{fig:li}
\end{figure}

\begin{figure}[ht]
    \includegraphics{little2014-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/USA data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/USA data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density. 
    }
    \label{fig:little}
\end{figure}

\begin{figure}[ht]
    \includegraphics{mccormack2002-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Malawi data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Malawi data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density. 
    }
    \label{fig:mccormack}
\end{figure}

\begin{figure}[ht]
    \includegraphics{niculescu2015-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Romania data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Romania data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:niculescu}
\end{figure}

\begin{figure}[ht]
    \includegraphics{novitsky2014-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Botswana data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to HET/Botswana data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
        intervals. $x$-axis indicates regions of nonzero prior density.
    }
    \label{fig:novitsky}
\end{figure}

\begin{figure}[ht]
    \includegraphics{wang2015-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Beijing data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to MSM/Beijing data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% highest
        posterior density intervals. $x$-axis indicates regions of nonzero
        prior density.
    }
    \label{fig:wang}
\end{figure}

\begin{figure}[ht]
    \includegraphics{zetterberg2004-posterior}
    \caption[
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Estonia data with \software{netabc}.
    ]{
        Approximate marginal posterior distributions of \gls{BA} model
        parameters fitted to IDU/Estonia data with \software{netabc}. Vertical
        lines indicate posterior means, and shaded areas are 95\% highest
        posterior density intervals. $x$-axis indicates regions of nonzero
        prior density.
    }
    \label{fig:zetterberg}
\end{figure}

%<<abc_posterior, echo=FALSE, results="asis">>=
%    N <- 5000
%    replicate <- 0
%    for (m in c(2, 3, 4)) {
%    for (I in c(1000, 2000)) {
%    for (alpha in c(0, 0.5, 1, 1.5)) {
%        fn <- sprintf("{abc-posterior/%.1f_%d_%d_%d_%d}.pdf", alpha, I, m, N, replicate)
%        lab <- sprintf("fig:%.1f-%d-%d-%d-%d", alpha, I, m, N, replicate)
%        cat("\\begin{figure}[ht]\n")
%        cat("\\centering\n")
%        cat(paste0("\\includegraphics{", fn, "}\n"))
%        cat(sprintf("\\caption[Approximate marginal posterior distributions of BA model parameters for a simulated transmission tree with $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d.]{\n", alpha, I, m, N))
%        cat(sprintf("Approximate marginal posterior distributions of BA model parameters obtained by applying \\software{netabc} to a simulated transmission tree with BA parameter values $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d. Vertical dashed lines indicate true values. Shaded areas are 95\\%% highest posterior density intervals. $x$-axes indicate regions of nonzero prior density.\n", alpha, I, m, N))
%        cat("}\n")
%        cat(paste0("\\label{", lab, "}\n"))
%        cat("\\end{figure}\n")
%        cat("\\clearpage\n\n")
%    }
%    }
%    }
%@

>>>>

%\clearpage
%
%\begin{figure}[ht]
%    \includegraphics{bctree-posterior}
%    \caption
%    [
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Canada data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Canada data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:bctree}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{cuevas2009-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to mixed/Spain data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to mixed/Spain data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:cuevas}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{grabowski2014-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Uganda data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Uganda data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:grabowski}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{kao2011-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Taiwan data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Taiwan data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:kao}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{li2015-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Shanghai data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Shanghai data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density. 
%    }
%    \label{fig:li}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{little2014-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/USA data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/USA data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density. 
%    }
%    \label{fig:little}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{mccormack2002-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Malawi data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Malawi data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density. 
%    }
%    \label{fig:mccormack}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{niculescu2015-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Romania data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Romania data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:niculescu}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{novitsky2014-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Botswana data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to HET/Botswana data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% \gls{HPD}
%        intervals. $x$-axis indicates regions of nonzero prior density.
%    }
%    \label{fig:novitsky}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{wang2015-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Beijing data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to MSM/Beijing data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% highest
%        posterior density intervals. $x$-axis indicates regions of nonzero
%        prior density.
%    }
%    \label{fig:wang}
%\end{figure}
%
%\begin{figure}[ht]
%    \includegraphics{zetterberg2004-posterior}
%    \caption[
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Estonia data with \software{netabc}.
%    ]{
%        Approximate marginal posterior distributions of \gls{BA} model
%        parameters fitted to IDU/Estonia data with \software{netabc}. Vertical
%        lines indicate posterior means, and shaded areas are 95\% highest
%        posterior density intervals. $x$-axis indicates regions of nonzero
%        prior density.
%    }
%    \label{fig:zetterberg}
%\end{figure}
%
%<<abc_posterior, echo=FALSE, results="asis">>=
%    N <- 5000
%    replicate <- 0
%    for (m in c(2, 3, 4)) {
%    for (I in c(1000, 2000)) {
%    for (alpha in c(0, 0.5, 1, 1.5)) {
%        fn <- sprintf("{abc-posterior/%.1f_%d_%d_%d_%d}.pdf", alpha, I, m, N, replicate)
%        lab <- sprintf("fig:%.1f-%d-%d-%d-%d", alpha, I, m, N, replicate)
%        cat("\\begin{figure}[ht]\n")
%        cat("\\centering\n")
%        cat(paste0("\\includegraphics{", fn, "}\n"))
%        cat(sprintf("\\caption[Approximate marginal posterior distributions of BA model parameters for a simulated transmission tree with $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d.]{\n", alpha, I, m, N))
%        cat(sprintf("Approximate marginal posterior distributions of BA model parameters obtained by applying \\software{netabc} to a simulated transmission tree with BA parameter values $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d. Vertical dashed lines indicate true values. Shaded areas are 95\\%% highest posterior density intervals. $x$-axes indicate regions of nonzero prior density.\n", alpha, I, m, N))
%        cat("}\n")
%        cat(paste0("\\label{", lab, "}\n"))
%        cat("\\end{figure}\n")
%        cat("\\clearpage\n\n")
%    }
%    }
%    }
%@
